基于BSSMF矩阵分解的图像降噪方法

### 2025-03-28 paper/paper.tex
add some text

% Title and Author
\title{Final Paper Title}
\author{Your Name}
\date{\today}

@@

\begin{abstract}
This is the abstract of your paper. Provide a brief summary of the content, objectives, and conclusions of your work.
\end{abstract}

\section{Introduction}
Introduce the topic of your paper. Provide background information and state the objectives of your work.

\section{Related Work}
Discuss previous research or work related to your topic. Cite relevant sources, such as \cite{GOYAL2020220}.

\section{Methodology}
Explain the methods or approaches used in your work. Provide enough detail for reproducibility.\cite{Fan2019}

\section{Results}
Present the results of your work. Use tables, figures, and equations as needed.\cite{中值滤波}

\section{Discussion}
Interpret the results and discuss their implications. Compare with related work if applicable.

\section{Conclusion}
Summarize the main findings of your paper and suggest future work.

>>>>

% Title and Author
\title{基于BSSMF矩阵分解的图像降噪方法}
\author{王伟钊}
\date{\today}

@@

\begin{abstract}

\end{abstract}

\tableofcontents

\section{绪论}
图像降噪是图像处理中的一个重要问题，它在图像处理、计算机视觉、模式识别等领域有着广泛的应用。图像降噪的目的是去除图像中的噪声，使图像更加清晰，便于后续的处理。图像降噪的方法有很多，包括基于小波变换的方法、基于局部统计特性的方法、基于矩阵分解的方法等。本文提出了一种基于BSSMF矩阵分解的图像降噪方法，该方法利用了图像的低秩性和稀疏性，通过分解图像矩阵为低秩矩阵和稀疏矩阵的和，实现了对图像的降噪。

\subsection{问题描述}
在数学上，图像降噪问题可以用如下数学表达式描述\cite{SVDWhiteNoise}：
\begin{equation}
    A(i,j)=A_{0}(i,j)+N(i,j)
\end{equation}
其中$A(i,j)$是观测到的图像，$A_{0}(i,j)$是原始图像，$N(i,j)$是高斯白噪声(Addctive White Gaussian Noise, AWGN)\cite{AWGN}。

\subsection{国内外研究现状}
\subsubsection{基于传统滤波器的方法}
\subsubsection{基于小波变换的方法}
\subsubsection{基于深度学习的方法}

\section{相关工作}

\section{实验设计}

\section{实验结果与分析}

\section{结论}
